Safe Transferable Regions

### 2016-07-03 paper/introduction.tex
Wording.

Indeed, the utility of our approach described above is predicated
on the assumption that we can enforce certain invariants on
transferable regions. Firstly, a transferable region cannot be
transferred/freed inside an open block of that region (i.e, while it
is still open).  Secondly, a transferred/freed region cannot be
opened. These are typestate invariants on the transferable region
objects, which are hard to enforce statically due to the presence of
unrestricted aliasing. Techniques like linear types and unique
pointers can be used to restrict aliasing, but the constraints they
impose are often hard to program around. We therefore enforce
typestate invariants at runtime via lightweight checks. In
particular, we define an acceptable state transition discipline for
transferable regions (Fig.~\ref{fig:region-fsm}), and check, at
runtime, whether a given transition of a transferable region (\eg,
from \emph{open} state to \emph{freed} state) is valid or not. The
check is lightweight since it only involves checking a single tag that
captures the current state.  We believe that this is a reasonable
choice since regions are coarse-grained objects manipulated
infrequently, when compared to the fine-grained objects that are
present inside these regions, for which safety is enforced statically.
An added advantage of delegating the enforcement of typestate
invariants to runtime is that our region type system is
simple\footnote{Supplement lists all the type rules of our language,
which occupy less than a page.}, which made it possible to formulate a
type inference that completely eliminates the need to write region
type annotations. This, we believe, significantly reduces the
impediment to adopt our approach in practical setting.

>>>>

Indeed, the utility of our approach described above is predicated
on the assumption that we can enforce certain invariants on
transferable regions. Firstly, a transferable region cannot be
transferred/freed inside an open block of that region (i.e, while it
is still open).  Secondly, a transferred/freed region cannot be
opened. These are typestate invariants on the transferable region
objects, which are hard to enforce statically due to the presence of
unrestricted aliasing. Techniques like linear types and unique
pointers can be used to restrict aliasing, but the constraints they
impose are often hard to program around. We therefore enforce
typestate invariants at runtime via lightweight checks. In
particular, we define an acceptable state transition discipline for
transferable regions (Fig.~\ref{fig:region-fsm}), and check, at
runtime, whether a given transition of a transferable region (\eg,
from \emph{open} state to \emph{freed} state) is valid or not. The
check is lightweight since it only involves checking a single tag that
captures the current state.  We believe that this is a reasonable
choice since regions are coarse-grained objects manipulated
infrequently, when compared to the fine-grained objects that are
present inside these regions, for which safety is enforced statically.
An added advantage of delegating the enforcement of typestate
invariants to runtime is that our region type system is
simple\footnote{The accompanying material lists all the type rules of our language,
which occupy less than a page.}, which made it possible to formulate a
type inference that completely eliminates the need to write region
type annotations. This, we believe, significantly reduces the
impediment to adopt our approach in practical setting.
